---
title: "Homework 1"
subtitle: "`ggplot2` & `dplyr` Fundamentals · Quarto Blogging"
author: Sophia Stang
date: 2026-02-18
format:
  html:
    toc: true
---


## Ice Cream Blog


```{r}
library(tidyverse)
library(ggplot2)
```


```{r}
ice_cream <- read_csv("https://bcdanl.github.io/data/ben-and-jerry-cleaned.csv")
```

```{r}
head(ice_cream)
```

## Flavor Price Descriptions

```{r}
ice_cream|>
  arrange(
    desc(priceper1)
  )
```

```{r}
ggplot(data = ice_cream,
       mapping = aes(
         y = flavor_descr
       ))+
  geom_bar()
```

The range of popularity for the flavors is very wide.

```{r}
pop_flavors<- ice_cream|>
  count(flavor_descr, name = "n")|>
  filter(
    n>400
  )|>
  arrange(
    desc(n)
  )|>
  head(10)
```

```{r}
ggplot(data = pop_flavors,
       mapping = aes(
       x = n,
       y = flavor_descr))+
  geom_col()
```

The ten most popular flavors are listed above. Among them, Cherry Garcia is the most popular flavor.

```{r}
price_by_flav <- ice_cream|>
  filter(
    size1_descr == "16.0 MLOZ"
  )|>
  group_by(flavor_descr)|>
  summarise( n = n(),
             mean_price = mean(priceper1)
  )
```

```{r}
ggplot(data = price_by_flav,
       mapping = aes(
         x = n,
         y = mean_price
       ))+
  geom_point()
```


There is no clear relationship between popular flavors and their average prices


```{r}
tot_prices <- ice_cream|>
  mutate(
    price_paid = priceper1 - couponper1
  )|>
  group_by(
    household_income, region
  )|>
  summarize(
    mean_price_paid = mean(price_paid), .groups = "drop"
  )
```


```{r}
ggplot(data = tot_prices,
       mapping = aes(
        x = household_income,
        y = mean_price_paid,
        fill = household_income
       ))+
  geom_col()+
    facet_wrap(~region)
```

The `echo: false` option disables the printing of code (only output is displayed).

The price paid for Ben and Jerry's ice cream is similar among households. There are minimal differences among regions in the United States. 
